% This sample file is dedicated to the public domain.
\documentclass[12pt]{myucthesis}

%\nofiles
% The above command prevents latex from writing its auxiliary
% files. This is useful if you want to manually tweak them before you
% generate your final PDF.


% Page layout. The fancyhdr package may complain about the need for a
% larger headheight, depending on how long chapter titles are; if left
% unspecified in the geometry setup, it defaults to 12pt. The
% "showframe" option causes the geometry package (version >= 5.0) to
% show a frame around the margins on every page, which is great for
% checking that you don't overflow anywhere.

%\usepackage[letterpaper,includehead,margin=1in,headheight=15pt,showframe]{geometry}
\usepackage[letterpaper,includehead,margin=1in,headheight=15pt]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\lhead[\fancyplain{\thepage}{\thepage}]{\fancyplain{}{\scshape\rightmark}}
\rhead[\fancyplain{}{\scshape\leftmark}]{\fancyplain{\thepage}{\thepage}}
\chead{}
\cfoot{}
\lfoot{}
\rfoot{}


% Bibliography stuff:
\newcommand{\newblock}{\par} % need this for some natbib internal bug
\usepackage{natbib}
\citestyle{aa}
\bibliographystyle{yahapj}
\setlength{\bibsep}{0ex} % single-space entries
\def\bibpreamble{\addcontentsline{toc}{chapter}{Bibliography}} % get a good TOC entry


% Other setup:

\usepackage[T1]{fontenc} % see http://tinyurl.com/67zdxwf
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue,pdfusetitle]{hyperref}
\usepackage{pdflscape} % allows landscape-oriented figures with PDF page rotation
\usepackage{aasmacros,amsmath,amssymb,graphicx,caption}
\usepackage{mydeluxetable} % deluxetable customized to play well with ucthesis
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[figuresright]{rotating}
\usepackage{ctable}
\usepackage{comment}
\usepackage{bm}
\usepackage{xparse}

%Math stuff from Danny
\NewDocumentCommand{\evalat}{sO{\big}mm}{%
  \IfBooleanTF{#1}
   {\mleft. #3 \mright|_{#4}}
   {#3#2|_{#4}}%
}

% Math Shortcuts from Adrian
\newcommand{\x}{\mathbf{x}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\e}{\mathbf{e}}
\newcommand{\p}{\mathbf{p}}
\newcommand{\phat}{\widehat{\mathbf{p}}}
\newcommand{\C}{\mathbf{C}}
\newcommand{\Chat}{\mathbf{\widehat{C}}}
\newcommand{\F}{\mathbf{F}}
\newcommand{\Fhat}{\mathbf{\widehat{F}}}
\newcommand{\Q}{\mathbf{Q}}
\newcommand{\I}{\mathbf{I}}

% Math shortcuts from James
\newcommand{\invC}{\ensuremath{\C^{-1}}}
\newcommand{\dC}[1]{\ensuremath{\C_{,#1}}}
\DeclareMathOperator{\Tr}{tr}
\newcommand{\half}{\ensuremath{\frac{1}{2}}}
\newcommand{\PDeriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}

% Math shortcuts from Danny
\newcommand{\Prob}{\mathbf{P}}


\begin{document}
\ssp % single spacing
\hypersetup{pageanchor=false}
\include{setup}
\maketitle
\copyrightpage

\begin{abstract}
The Epoch of Reionization is one of the last unexplored eras of our Universe's history. Beginning about a billion years after the Big Bang, this epoch is characterized by the births of the first stars and galaxies, whose light subsequently altered the nature of the gas surrounding them. There are several experiments aiming to detect the phase transition of this gas as it changes from neutral hydrogen to ionized hydrogen. Such a detection would open a wealth of information about our early Universe, revealing details about the nature of the first luminous sources and the evolution of structure formation.

Interferometers such as the Precision Array for Probing the Epoch of Reionization (PAPER) and the Hydrogen Epoch of Reionization Array (HERA) seek to measure the 21\,cm signal from neutral hydrogen and map its evolution over spatial and temporal scales. A detection of reionization, however, is a difficult measurement. Though the 21\,cm signal is a powerful 3D probe of the intergalactic medium, it is easily buried underneath bright foreground signals and instrumental systematics. A clean detection of reionization is ambitious and requires analysis methods that maximize data sensitivity and increase confidence in results.

The work presented in this thesis addresses many of the key challenges that face the current field of 21\,cm cosmology. This includes algorithms to locate contaminated data, methods to ensure accurate power spectrum measurements, and techniques for removing unwanted systematics while preserving the reionization signal. These developments serve as the foundation of the latest 21\,cm measurements from the PAPER-64 and PAPER-128 arrays, whose results lie near the forefront of the field. These methods are also fundamental to HERA and future experiments, as they provide a strong foundation for the continued exploration of our cosmic dawn.

\end{abstract}

\hypersetup{pageanchor=true}
\begin{frontmatter}

\begin{dedication}
\null\vfil
{\large
\begin{center}
\textit{to my parents}
\end{center}}
\null\vfil
\end{dedication}

\tableofcontents
\listoffigures % optional
\listoftables % optional

% If using code.sty, can also add:
%% \listofcodes
%% \addcontentsline{toc}{chapter}{List of Code Examples}

\begin{acknowledgements}
% Feel free to modify or remove this acknowledgment:
%This dissertation was typeset using the
%\href{https://github.com/pkgw/ucastrothesis}{\textsf{ucastrothesis}}
%\LaTeX\ template.
There is no easy way to sum up my time in astronomy. This thesis represents a concrete collection of my work over the past six years, but it's impossible to summarize the joys, tears, laughter, frustrations, and friendships that have accompanied it along the way.

Graduate school has opened my world to a beautiful, enigmatic universe, but it has also given back to me in countless ways. It's instilled in me determination and perseverance to conquer difficult, abstract problems. It's given me a unique voice and boundless joy through teaching and outreach experiences. And it's shaped my perspective of science and discovery, helping me to find comfort in ambiguity and embrace the unexpected.

For these things (and much more), I have many people to thank. 

First, I must thank my research advisor, Aaron Parsons. Thank you for the hours spent de-bugging code next to me, the days of teaching me how to think intuitively (and in Fourier-space), the months of conversations about signal loss, the years of radio astronomy excitement, and most importantly, for giving me confidence in my abilities always. 

Throughout my time in astronomy at UCLA and Berkeley I have had the privilege of working with many other influential people who have played an advisory and supportive role in my work and life: James Aguirre, Josh Dillon, Alex Filippenko, Steve Furlanetto, Andrea Ghez, Jonnie Pober, and especially Danny Jacobs (thank you for being there for me during the low lows, for advocating for my work, and for generally being a second advisor and mentor who I can always count on for support, guidance, and funny quotes) and Adrian Liu (you've been a huge role model both in terms of research and teaching, and I have so appreciated your positive attitude, your willingness to always help, and yes, your mathematical proofs and lessons).

Thank you also to the PAPER and HERA collaborations. It's been wonderful to work amongst intelligent, passionate scientists, and I am grateful to have made many friends along the way, including Saul Kohn and Matt Kolopanis, who know better than anyone else the complex, emotional journey we took as graduate students working on PAPER - I'm so glad we were on the ride together.

The Berkeley Astronomy Department truly feels like home, and I am appreciative of everyone who has shaped my career, taught me science, and made me feel welcome. This includes instructors of my classes, faculty on my prelim, qual, and thesis committees, department staff (especially Nina Ruymaker and Lochland Trotter for supporting my Astro Night visions, and Dexter Stewart for all the smiles and bureaucratic magic), and of course, my fellow department peers. 

The work in this thesis would also not have been possible without financial support. Thank you to the NSF, the Gordon and Betty Moore Foundation, and the South African Radio Astronomy Observatory for supporting the PAPER and HERA experiments. I am also grateful for the NSF GRFP and UC Berkeley Chancellor's Fellowship, which both chose to invest in me.

Finally, this work would not have been possible without my friends and family. I am lucky to be surrounded by old and new lifelong friends who have worked alongside me, played alongside me, and made me a better person through it all. To my life partner, Zaki Ali, who has steadfastly supported me both professionally and personally, and who is perhaps the best thing to come out of graduate school. And last but not least, to my Mom and Dad, who are in everything I do and who inspire everything I do. I love you all.

As I close this chapter of my life, I can't help but think about a moment from a decade ago, when I sat in my very first astronomy class. I remember being consumed with a feeling of smallness as I tried to comprehend the overwhelming size of the universe. But at the same time, I felt powerful and inspired by the sheer capability, technology, and teamwork that together has opened up a window into our universe - where we are actually able to study extraordinary phenomena and physics - and I will forever be grateful to have gotten to play a small role in unraveling its mysteries. Thank you all for the adventure.

\end{acknowledgements}
\end{frontmatter}

\include{intro/intro}
\include{methods_PS/methods_PS}
\include{PSA64/PSA64}
\include{PSA64_results/PSA64_results}
\include{PSA128/PSA128}
\include{Future/Future}
\include{conclusion/conclusion}
\bibliography{thesis}{}

\end{document}
